\documentclass{article}
\usepackage[utf8]{inputenc}

\input{header.tex}
\title{Philosophy of Science in Engineering\\
42610\\
TA: Malthe Haulund Elkær}
\author{Magnus Søborg-Madsen s144063\\Roar Nind Steffensen s144107\\Sebastian Lindhard Budsted s135243\\
Units: 7525}

\date{November 2017}

\begin{document}

\maketitle


\section{Introduction}

Within few years, driverless vehicles will enter the market. An important question is which ethical principles should an operating system of such a car follow? In this paper, we analyze a suggestion by a fictive politician, using theory and knowledge gained in the DTU course 42610 Philosophy of Science in Engineering.


\textbf{Politician's suggestion:}
\textit{"It should be legal in the European Union to sell, import and use driverless vehicles programmed to navigate in accordance with only principle PP in the event of unavoidable crash."}

\textbf{Principle PP:} 
\textit{"Choose the outcome that most likely will result in the greatest potential for safety for the vehicle’s passengers." }

% \newpage

\section{Argument}

\textbf{Premises:}
\begin{enumerate}
\item All lives should be treated  equally.

\item Given the unavoidable choice between losing $N_1$ number of lives or $N_2$ number of lives, the fewest should be chosen.

\item Given the unavoidable choice between killing $N_1 = 1$ passenger or $N_2 = 10$ bystanders, a car programmed in accordance with only principle PP will choose to kill $N_2 = 10$ bystanders.

\item If it becomes to legal to sell, import and use driver-less programmed to navigate in accordance with only principle PP, a car may kill $N_2 = 10$ bystanders instead of $N_1 = 1$ passenger.

\end{enumerate}

\textbf{Conclusion:} It should \underline{not} be legal to sell, import and use driver-less programmed to navigate in accordance with only principle PP in the event of unavoidable crash.

\input{revised.tex}
%\input{justification_default.tex}
%\input{justification_Roar.tex}
%\input{justification_Magnus.tex}
%\input{justification_seblind.tex}

\bibliographystyle{unsrt}
\bibliography{bibliography}

\end{document}
